The Effect of Events on Australian Parliamentary Discussion (1870--2017)

### 2018-10-02 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Add NSW scraping addresses and clean up literature and minor improvements to paper

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Australian Parliamentary Discussion (1870--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. We then use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time. Finally, we examine the effect of various events using a Bayesian choice model. We find that: 1) elections are associated with topic changes only when the party in power changes but a change in government sometimes does not require this to be associated with topic changes; and 2) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorism. Our findings have implications for how we think about the longer-term trajectory of government policy as the media cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release. Additionally, there is a more limited set of XML records available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like. There are 65,000 **[UPDATE]** days worth of publicly available Hansard records across the state and federal parliaments (Table \ref{tab:yearsusedtable}). Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).

@@

missing_days %>% 
  kable(booktabs = T, caption = "Missing days") %>%
  kable_styling(font_size = 8)

@@

governments %>% 
  kable(booktabs = T, caption = "Change in governments") %>%
  kable_styling(font_size = 8)

@@

elections %>% 
  filter(election == 1) %>% 
  select(year, electionDate, electionWinner) %>% 
  kable("latex", booktabs = T, caption = "Elections") %>%
  kable_styling(font_size = 8)

@@

keyEconomicDates %>% 
  kable(booktabs = T, caption = "Key economic events") %>%
  kable_styling(font_size = 8)

@@

keyOtherDates %>% 
  kable(booktabs = T, caption = "Key other events") %>%
  kable_styling(font_size = 8)

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Australian Parliamentary Discussion (1870--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. We then use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and steady changes over time. Finally, we consider various events using Bayesian regression with a Dirichlet-distributed response variable. We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks. Our findings have implications for how we think about the longer-term trajectory of government policy as the media cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release. Additionally, there is a more limited set of XML records available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like. There are roughly 54,331 **[UPDATE]** days worth of publicly available Hansard records across the state and federal parliaments (Table \ref{tab:yearsusedtable}). Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).

@@

missing_days %>% 
  kable(booktabs = T, caption = "Missing days") %>%
  kable_styling(font_size = 12)

@@

governments %>% 
  kable(booktabs = T, caption = "Change in governments") %>%
  kable_styling(font_size = 12)

@@

elections %>% 
  filter(election == 1) %>% 
  select(year, electionDate, electionWinner) %>% 
  kable("latex", booktabs = T, caption = "Elections") %>%
  kable_styling(font_size = 12)

@@

keyEconomicDates %>% 
  kable(booktabs = T, caption = "Key economic events") %>%
  kable_styling(font_size = 12)

@@

keyOtherDates %>% 
  kable(booktabs = T, caption = "Key other events") %>%
  kable_styling(font_size = 12)

### 2018-10-02 outputs/docs/events/svm-rmarkdown-article-example.tex
Add NSW scraping addresses and clean up literature and minor improvements to paper

\title{The Effect of Events on Australian Parliamentary Discussion (1870--2017) \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 30
September 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\noindent We systematically analyse how parliamentary discussion changes in
response to different types of events in Australian history. We first
compile a dataset of what was said in Australian state and federal
parliaments from the mid-1800s through to 2017 based on available public
records. We then use a structural text model to reduce the
dimensionality of the text and to impose prior knowledge such as
correlation between days and changes over time. Finally, we examine the
effect of various events using a Bayesian choice model. We find that: 1)
elections are associated with topic changes only when the party in power
changes but a change in government sometimes does not require this to be
associated with topic changes; and 2) economic events, such as financial
crises, have less significant and persistent effects than other events
such as terrorism. Our findings have implications for how we think about
the longer-term trajectory of government policy as the media cycle
becomes increasingly focused on short-term events.

@@

\caption{\label{tab:yearsusedtable}Hansard records used}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{lrrr}
\toprule
Parliament & House & Years used & Number of records\\
\midrule
Commonwealth & House of Representatives & 1901 - 2017 & 7873\\
 & Senate & 1901 - 2017 & TBD\\
Queensland & Legislative Assembly & 1860 - 2017 & 9699\\
 & Legislative Council & 1860 - 1922 & 4156\\
New South Wales & Legislative Assembly & 1856 - 2017 & TBD\\
\addlinespace
 & Legislative Council & 1856 - 2017 & TBD\\
Victoria & Legislative Assembly & 1856 - 2017 & TBD\\
 & Legislative Council & 1851 - 2017 & TBD\\
Tasmania & House of Assembly & 1856 - 2017 & TBD\\
 & Legislative Council & 1856 - 2017 & TBD\\
\addlinespace
South Australia & House of Assembly & 1857 - 2017 & TBD\\
 & Legislative Council & 1840 - 2017 & TBD\\
Western Australia & Legislative Assembly & 1890 - 2017 & TBD\\
 & Legislative Council & 1832 - 2017 & TBD\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\title{The Effect of Events on Australian Parliamentary Discussion (1870--2017) \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 02
October 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\noindent We systematically analyse how parliamentary discussion changes in
response to different types of events in Australian history. We first
compile a dataset of what was said in Australian state and federal
parliaments from the mid-1800s through to 2017 based on available public
records. We then use a structural text model to reduce the
dimensionality of the text and to impose prior knowledge such as
correlation between days and steady changes over time. Finally, we
consider various events using Bayesian regression with a
Dirichlet-distributed response variable. We find that: 1) elections are
associated with topic changes only when the party in power changes; 2) a
change in government can be associated with topic changes even if the
party in power does not change; 3) economic events, such as financial
crises, have less significant and persistent effects than other events
such as terrorist attacks. Our findings have implications for how we
think about the longer-term trajectory of government policy as the media
cycle becomes increasingly focused on short-term events.

@@

\caption{\label{tab:yearsusedtable}Hansard records used}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{lrrr}
\toprule
Parliament & House & Years used & Number of records\\
\midrule
Commonwealth & House of Representatives & 1901 - 2017 & 7873\\
 & Senate & 1901 - 2017 & TBD\\
Queensland & Legislative Assembly & 1860 - 2017 & 9699\\
 & Legislative Council & 1860 - 1922 & 4156\\
New South Wales & Legislative Assembly & 1879 - 2017 & 8903\\
\addlinespace
 & Legislative Council & 1879 - 2017 & 6463\\
Victoria & Legislative Assembly & 1856 - 2017 & -\\
 & Legislative Council & 1851 - 2017 & -\\
Tasmania & House of Assembly & TBD - 2017 & TBD\\
 & Legislative Council & TBD - 2017 & TBD\\
\addlinespace
South Australia & House of Assembly & TBD - 2017 & TBD\\
 & Legislative Council & TBD - 2017 & TBD\\
Western Australia & Legislative Assembly & 1890 - 2017 & 5977\\
 & Legislative Council & 1870 - 2017 & 5725\\
\bottomrule
\end{tabular}
\end{table}
